---
title: "Spatial Relations Experiment"
author: "Js Lucas"
date: "18/8/2020"
output: 
  html_document:
    toc: true
    toc_float:
      toc_collapsed: true
    toc_depth: 3
    number_sections: true
    theme: cosmo
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(dplyr)
library(sf)
library(readr)
library(leaflet)
library(stringr)
library(plotly)
library(units)
```

# Introduction

Motivations

```{r}
drawings <- st_read('data/drawings_2.csv', options=c("GEOM_POSSIBLE_NAMES=geometry"), crs = 4326) %>% 
  select(-geom)

drawings$geometry <- drawings %>% 
  st_geometry() %>% 
  st_make_valid()

drawings_resp <- drawings %>% 
  filter(!(userid  %in% c("0", "-1")))

drawings_resp <- drawings_resp %>%
  group_by(userid) %>% 
  filter(n() == 20)

drawings_fun <- drawings %>% 
  filter(userid == "-1")
```
## The Experiment

Experiment design

Translation of the relation names

# 1. What is the general form of the drawings made by participants?

Usage of types of polygons

```{r}
as.data.frame(drawings_resp) %>% 
  group_by(relation, geometry_type) %>% 
  summarise(n = n()) %>% 
  plot_ly(x = ~relation, y= ~n, type = 'bar', color = ~geometry_type)
```

There are lines!
How many participants drew them?

```{r}
as.data.frame(drawings_resp) %>% 
  filter(geometry_type == 'MultiLineString' | geometry_type == 'LineString') %>% 
  distinct(userid) %>% 
  count()
```

```{r}
plot_all_drawings <- function(dataframe, long, latit, zoomLevel){
  leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = st_geometry(dataframe),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>% 
  setView(lng = long, lat = latit, zoom = zoomLevel)  
}
```

## Examples
Lets get a general view of the data

### IN FRONT OF Maria Pitanga
```{r}
drawings_resp %>%
  filter(relation == "NA FRENTE DE" & landmark == "Maria Pitanga") %>% 
  plot_all_drawings(-35.8793534, -7.2238664, 18)
```

### NEXT TO Maria Pitanga
```{r}
drawings_resp %>%
  filter(relation == "AO LADO DE" & landmark == "Maria Pitanga") %>% 
  plot_all_drawings(-35.8793534, -7.2238664, 18)
```

### AT Bar do Cuscuz STREET, NEAR Maria Pitanga
```{r}
drawings_resp %>%
  filter(relation == "NA RUA - PERTO DE" & landmark == "Maria Pitanga") %>% 
  plot_all_drawings(-35.8793534, -7.2238664, 18)
```

### RIGHT OF Maria Pitanga
```{r}
drawings_resp %>%
  filter(relation == "À DIREITA DE" & landmark == "Maria Pitanga") %>% 
  plot_all_drawings(-35.8793534, -7.2238664, 18)
```


### Between Café Poético and Bar do Cuscuz
```{r}
drawings_resp %>%
  filter(relation == "ENTRE" & landmark == "Café Poético") %>% 
  plot_all_drawings(-35.8793534, -7.2238664, 18)
```

## Outliers?

Let's examine drawings by area

```{r}
drawings_resp$area <- st_area(st_geometry(drawings_resp))

as.data.frame(drawings_resp) %>% 
  plot_ly(x = ~landmark , y = ~area, type = 'box', color = ~relation) %>% 
  layout(boxmode='group')
```

As expected, the relations BETWEEN and AT STREET - NEAR contain the drawings with more area. Lets have a closer look at the really big ones.

```{r}
drawings_resp %>%
  filter(area > set_units(15000, m^2)) %>% 
  plot_all_drawings(-35.87363, -7.23018, 15)
```

It seems that there is nothing weird about them.

# 2. Corner vs Non Corner
## The usage of multipolygons is different for each class of landmarks?

Our assumption is that for landmarks located at street corners, participants will draw more multipolygons, since they might feel uncertain to which of the streets correspond to the relation.

```{r}
as.data.frame(drawings_resp) %>% 
  mutate(location = if_else(landmark %in% c("Localiza Hertz", "Maria Pitanga"), "Corner", "Non-Corner")) %>% 
  group_by(location, geometry_type) %>% 
  summarise(n = n()) %>% 
  plot_ly(x = ~location, y= ~n, type = 'bar', color = ~geometry_type)
```

The usage of geometry types seems to be the same.
Now let's examine by relation.

```{r}
drawings_resp$relation %>% 
  unique() %>% 
  lapply(function(rel){
    as.data.frame(drawings_resp) %>%
      filter(relation == rel) %>% 
      mutate(location = if_else(landmark %in% c("Localiza Hertz", "Maria Pitanga"), "Corner", "Non-Corner")) %>% 
      group_by(location, relation, geometry_type) %>% 
      summarise(n = n()) %>% 
      plot_ly(x = ~location, y= ~n, type = 'bar',
              color = ~geometry_type, legendgroup = ~geometry_type,
              showlegend = (rel == "ENTRE")) %>% 
      add_annotations(
        text = rel,
        xref = "paper",
        yref = "paper",
        yanchor = "middle",
        xanchor = "center",
        align = "center",
        x = 0.5,
        y = 1,
        showarrow = FALSE)
  }) %>% 
  subplot(nrows = 3, margin = .03, shareY = TRUE)


```

This pattern continues for all the relations.
One relation where we didn't expect to see multipolygons was IN FRONT OF.

```{r}
leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = st_geometry(as.data.frame(drawings_resp) %>%
                                   filter(relation == "NA FRENTE DE" &
                                            geometry_type == "MultiPolygon" &
                                            landmark == "Café Poético") %>% 
                                   slice(1) %>% 
                                   st_as_sf()),
              color = "#3498db", weight = 2, fillOpacity = .2) %>% 
  addPolygons(data = st_geometry(as.data.frame(drawings_resp) %>%
                                   filter(relation == "NA FRENTE DE" &
                                            geometry_type == "MultiPolygon" &
                                            landmark == "Café Poético") %>% 
                                   slice(2) %>% 
                                   st_as_sf()),
              color = "#e74c3c", weight = 2, fillOpacity = .2) %>%
  addPolygons(data = st_geometry(as.data.frame(drawings_resp) %>%
                                   filter(relation == "NA FRENTE DE" &
                                            geometry_type == "MultiPolygon" &
                                            landmark == "Café Poético") %>% 
                                   slice(3) %>% 
                                   st_as_sf()),
              color = "#f1c40f", weight = 2, fillOpacity = .2) %>%
  setView(lng = -35.87965, lat = -7.22414, zoom = 18)
```

```{r}
leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = st_geometry(as.data.frame(drawings_resp) %>%
                                   filter(relation == "NA FRENTE DE" &
                                            geometry_type == "MultiPolygon" &
                                            landmark == "Maria Pitanga") %>% 
                                   slice(1) %>% 
                                   st_as_sf()),
              color = "#3498db", weight = 2, fillOpacity = .2) %>% 
  addPolygons(data = st_geometry(as.data.frame(drawings_resp) %>%
                                   filter(relation == "NA FRENTE DE" &
                                            geometry_type == "MultiPolygon" &
                                            landmark == "Maria Pitanga") %>% 
                                   slice(2) %>% 
                                   st_as_sf()),
              color = "#e74c3c", weight = 2, fillOpacity = .2) %>%
  setView(lng = -35.87965, lat = -7.22414, zoom = 18)
```

Turns out our assumption was partially correct, for this also happened for non corner places. We suppose that this could be due to proximity to the streets, a more thorough analysis needs be done to allow any conclusion on the subject.

# 3. Which Frame of Reference do People Often have in Mind?
What exactly does one mean, when it said that one object is "to the right" of another?
To the right might be interpreted as at the rightside from the object's perspective, 
or from the perspective of an observer, that is positioned in front of the object.
The former interpretation, uses a Frame of Reference (FoR) named "Allocentric", while the latter uses the
"Egocentric".

We are interested in finding out, which of these two FoRs participants 
had in mind while drawing the relations and we can do this by analysing the relation
"TO THE RIGHT OF".

## Analysis of the "RIGHT OF" Relation

We do this by comparing the drawings with two buffer geometries. One that encompasses
the right side of the landmark, and another for the left side.

We assume the egocentric FoR for our geometries, thus, if a drawing
is found to be in the right buffer, it means that the reasoning of the participant
fits in the **egocentric** category. If however the drawing is in the left buffer,
the **allocentric** FoR better represents the participants' thought process.

```{r}
for_analysis <- function(left_buffer, right_buffer, target_landmark){
  both_sides_buffer <- st_union(left_buffer, right_buffer)
  
  right_of <- drawings_resp %>% 
    filter(relation == "À DIREITA DE" & landmark == target_landmark)
  
  right_of$right_int <- right_of %>% 
    st_geometry() %>% 
    st_intersects(right_buffer, sparse = FALSE)
  
  right_of$left_int <- right_of %>% 
    st_geometry() %>% 
    st_intersects(left_buffer, sparse = FALSE)
  
  right_of <- right_of %>% 
    mutate(both_int = right_int == left_int)
  
  # SUBSET OF ROWS TO COMPUTE INTERSECTION AREAS WITH THE RIGHT BUFFER
  right_of_r_int <- right_of  %>% 
    filter(right_int == TRUE)
  
  right_of_r_int$area <- right_of_r_int %>% 
    st_geometry() %>% 
    st_intersection(right_buffer) %>% 
    st_area()
  
  right_of <- right_of  %>% 
    merge(as.data.frame(right_of_r_int) %>%  select(id, area),
          by = "id", all.x = TRUE) %>%
    rename(area_r = area.y) %>% 
    mutate(area_r = if_else(is.na(area_r), set_units(0, m^2), area_r))
  
  rm(right_of_r_int)
  
  # SUBSET OF ROWS TO COMPUTE INTERSECTION AREAS WITH THE LEFT BUFFER
  right_of_l_int <- right_of  %>% 
    filter(left_int == TRUE)
  
  right_of_l_int$area <- right_of_l_int %>% 
    st_geometry() %>% 
    st_intersection(left_buffer) %>% 
    st_area()
  
  right_of <- right_of  %>% 
    merge(as.data.frame(right_of_l_int) %>%  select(id, area),
          by = "id", all.x = TRUE) %>%
    rename(area_l = area) %>% 
    mutate(area_l = if_else(is.na(area_l), set_units(0, m^2), area_l))
  
  rm(right_of_l_int)
  
  right_of <- right_of %>% 
    mutate(intersects = case_when(area_r > set_units(50, m^2) & area_l > set_units(50, m^2) ~ "BOTH",
                                  both_int & area_r < set_units(50, m^2) & area_l < set_units(50, m^2) ~ "BOTH",
                                  area_r > set_units(50, m^2) ~ "RIGHT",
                                  area_l > set_units(50, m^2) ~ "LEFT",
                                  area_r < set_units(50, m^2) & left_int ~ "LEFT",
                                  area_r < set_units(50, m^2) & !left_int ~ "RIGHT",
                                  area_l < set_units(50, m^2) & right_int ~ "RIGHT",
                                  area_l < set_units(50, m^2) & !right_int ~ "LEFT"))
  
  return(right_of)
}
```


### Niscar
```{r}
right_buffer <- st_read('{"type":"Polygon","coordinates":[[[-35.8698164543337,-7.23354689555164],[-35.8700657719415,-7.23375171630509],[-35.870310901112,-7.23345415553491],[-35.8700615836631,-7.2332493348928],[-35.8698164543337,-7.23354689555164]]]}', crs = 4326)
left_buffer <- st_read('{"type":"Polygon","coordinates":[[[-35.8700427811703,-7.23377962463979],[-35.8697934635476,-7.23357480387589],[-35.8695483338933,-7.23387236452473],[-35.8697976516749,-7.23407718539997],[-35.8700427811703,-7.23377962463979]]]}', crs = 4326)

right_niscar <- for_analysis(left_buffer, right_buffer, "Niscar")
```

```{r}
right_niscar %>%
  group_by(intersects) %>% 
  summarise(n = n()) %>% 
  plot_ly(values = ~n, labels = ~intersects) %>% 
  add_pie(hole = .6)
```

For the _Niscar_ landmark, most drawings (55%) are on the left buffer, which 
represents the **allocentric** FoR.

One interesting observation is that many (25%) participants chose to draw on both
sides.

```{r}
leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = right_buffer,
              color = "#3498db", weight = 2, fillOpacity = .001) %>% 
  addPolygons(data = st_geometry(right_niscar %>%
                                  filter(intersects == "RIGHT")),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>%
  setView(lng = -35.87003, lat = -7.23374, zoom = 18)

leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = left_buffer,
              color = "#3498db", weight = 2, fillOpacity = .001) %>% 
  addPolygons(data = st_geometry(right_niscar %>%
                                  filter(intersects == "LEFT")),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>%
  setView(lng = -35.87003, lat = -7.23374, zoom = 18)
```

### Café Poético
```{r}
right_buffer <- st_read('{"type":"Polygon","coordinates":[[[-35.87940238416194,-7.223747285824582],[-35.879239439964294,-7.224033334573388],[-35.878924280405045,-7.223838422306055],[-35.87908521294594,-7.223549712513339],[-35.87940238416194,-7.223747285824582]]]}', crs = 4326)
left_buffer <- st_read('{"type":"Polygon","coordinates":[[[-35.87943322956562,-7.223757264272369],[-35.879783257842064,-7.223936211065018],[-35.87960354983806,-7.224271486649396],[-35.87926559150219,-7.224051960997253],[-35.87943322956562,-7.223757264272369]]]}', crs = 4326)

right_cafe <- for_analysis(left_buffer, right_buffer, "Café Poético")
```

```{r}
right_cafe %>%
  group_by(intersects) %>% 
  summarise(n = n()) %>% 
  plot_ly(values = ~n, labels = ~intersects) %>% 
  add_pie(hole = .6)
```

For the second landmark (Café Poético) the values are closer to each other 
(7 drawings in the left buffer and 8 in the right one).

```{r}
leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = right_buffer,
              color = "#3498db", weight = 2, fillOpacity = .001) %>% 
  addPolygons(data = st_geometry(right_cafe %>%
                                  filter(intersects == "RIGHT")),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>%
  setView(lng = -35.8793534, lat = -7.2238664, zoom = 18)

leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = left_buffer,
              color = "#3498db", weight = 2, fillOpacity = .001) %>% 
  addPolygons(data = st_geometry(right_cafe %>%
                                  filter(intersects == "LEFT")),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>%
  setView(lng = -35.8793534, lat = -7.2238664, zoom = 18)
```

### Localiza Hertz

```{r}
right_buffer <- st_read('{"type":"Polygon","coordinates":[[[-35.87012529373169,-7.23396975742232],[-35.8697310090065,-7.233635819466916],[-35.87004616856575,-7.233251324861703],[-35.87044849991798,-7.233582602240051],[-35.87012529373169,-7.23396975742232]]]}', crs = 4326)
left_buffer <- st_read('{"type":"Polygon","coordinates":[[[-35.87009847164154,-7.23399104429556],[-35.86986780166626,-7.234271764842552],[-35.86948022246361,-7.233923192383596],[-35.869717597961426,-7.233649123772656],[-35.87009847164154,-7.23399104429556]]]}', crs = 4326)

right_localiza <- for_analysis(left_buffer, right_buffer, "Localiza Hertz")
```

```{r}
right_localiza %>%
  group_by(intersects) %>% 
  summarise(n = n()) %>% 
  plot_ly(values = ~n, labels = ~intersects) %>% 
  add_pie(hole = .6)
```

For the third landmark, the most drawings are in the left buffer. 

```{r}
leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = right_buffer,
              color = "#3498db", weight = 2, fillOpacity = .001) %>% 
  addPolygons(data = st_geometry(right_localiza %>%
                                  filter(intersects == "RIGHT")),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>%
  setView(lng = -35.87003, lat = -7.23374, zoom = 18)

leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = left_buffer,
              color = "#3498db", weight = 2, fillOpacity = .001) %>% 
  addPolygons(data = st_geometry(right_localiza %>%
                                  filter(intersects == "LEFT")),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>%
  setView(lng = -35.87003, lat = -7.23374, zoom = 18)
```

### Maria Pitanga

```{r}
right_buffer <- st_read('{"type":"Polygon","coordinates":[[[-35.879565328359604,-7.223766577490084],[-35.87934136390685,-7.224131123290164],[-35.879019498825066,-7.223914258488325],[-35.87923809885979,-7.223569669417386],[-35.879565328359604,-7.223766577490084]]]}', crs = 4326)
left_buffer <- st_read('{"type":"Polygon","coordinates":[[[-35.879617631435394,-7.2237945171421085],[-35.879974365234375,-7.224023356131708],[-35.8797624707222,-7.224405197676178],[-35.87940037250519,-7.224165715212135],[-35.879617631435394,-7.2237945171421085]]]}', crs = 4326)

right_maria <- for_analysis(left_buffer, right_buffer, "Maria Pitanga")
```

```{r}
right_maria %>%
  group_by(intersects) %>% 
  summarise(n = n()) %>% 
  plot_ly(values = ~n, labels = ~intersects) %>% 
  add_pie(hole = .6)
```

In the last landmark, the left buffer again has the majority of drawings, but by
a lesser difference.

```{r}
leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = right_buffer,
              color = "#3498db", weight = 2, fillOpacity = .001) %>% 
  addPolygons(data = st_geometry(right_maria %>%
                                  filter(intersects == "RIGHT")),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>%
  setView(lng = -35.8793534, lat = -7.2238664, zoom = 18)

leaflet() %>% 
  addTiles() %>% 
  addPolygons(data = left_buffer,
              color = "#3498db", weight = 2, fillOpacity = .001) %>% 
  addPolygons(data = st_geometry(right_maria %>%
                                  filter(intersects == "LEFT")),
              color = "#e74c3c", weight = 2, fillOpacity = .001) %>%
  setView(lng = -35.8793534, lat = -7.2238664, zoom = 18)

```

### All results

```{r}
right_all <- rbind(right_niscar, right_cafe, right_localiza,  right_maria)

as.data.frame(right_all) %>% 
  group_by(intersects, landmark) %>% 
  summarise(n = n()) %>% 
  plot_ly(y = ~n, x = ~landmark, type='bar', color = ~intersects)
```

Upon examining the combination of results, in most of the cases drawings of the
relation "RIGHT OF" intersected only with the left buffer, therefore the *allocentric*
FoR seem to be used more often by participants. However, the higher intersection 
with the right buffer for both Café Poético and Maria Pitanga raises questions. 
Might this result be affected by the geographical direction towards which the landmarks
are facing (Both Café Poético and Maria Pitanga are neighbors and face the same direction)?
What happens if we factor in people's problems in differencing left from right or
even map reading difficulties?

Another possible future work, would be to repeat this experiment, but showing 
participant's the actual images of landmarks facades.

# 4. How Similar Are the Areas Generated by the Proposed Algorithms and the Ones Made by the Participants?

In this paper (REFERENCE) we propose algorithms for automatically generating 
geometries representing different spatial relations. Now we try to evaluate their
performance by comparing them to the drawings made by participants of the experiment.

## Intersection of Areas

Here we verify if each drawing intersects the corresponding area (same landmark
and relation) produced by the implementation of the proposed algorithms.

```{r}
get_fun_geom <- function(rel, landm){
  return(drawings_fun %>% 
           filter(relation == rel & landmark == landm) %>% st_geometry())
}
```

```{r}
drawings_resp <- drawings_resp %>% 
  rbind(drawings_resp %>% 
          filter(relation == "À DIREITA DE") %>% 
          mutate(relation = "À DIREITA DE (ALLO)"))

drawings_resp <- drawings_resp %>% 
  rowwise() %>% 
  mutate(int_fun_c = st_intersects(get_fun_geom(relation, landmark), geometry, , sparse = FALSE)) %>% 
  st_as_sf()
```

```{r}
as.data.frame(drawings_resp) %>% 
  group_by(relation) %>% 
  summarise(true = sum(int_fun_c) / n(), false = (n() - sum(int_fun_c)) / n()) %>%
  plot_ly(y = ~relation, x = ~true,  type = "bar", name = "Intersect the Function Result") %>% 
  add_trace(x = ~false, name = "Do not Intersect the Function Result") %>% 
  layout(barmode = "stack")
```

The geometries generated by the algorithm intersect more than 50% of the drawings
in all relations, with the exception of the allocentric version of "TO THE RIGHT".

## Interseção com as ruas
During data collection, participants were told to draw the region they expected
a car to be in, after reading a describing sentence. However some participants, produced
areas in regions that are not streets.

The proposed algorithms, work in the scope of streets. So now we remove the drawings
that do not intersect with streets.

```{r include=FALSE}
streets_acude <- st_read('{"type":"MultiLineString","coordinates":[[[-35.8776727894036,-7.2228612081959],[-35.8787458,-7.2236093],[-35.8796217,-7.22420980000001]],[[-35.8796217,-7.22420980000001],[-35.8799062,-7.2244169],[-35.8801691,-7.22460180000001],[-35.8804894,-7.2248003],[-35.8808595,-7.22499809999999],[-35.8809824018697,-7.2250458005839]],[[-35.8796217,-7.22420980000001],[-35.8796861,-7.2230998],[-35.8797420702902,-7.22208071410284]],[[-35.8800953,-7.2242459],[-35.8801813,-7.22314700000001],[-35.8802334898354,-7.22227063091145]]]}', crs = 4326)

streets_acude <- streets_acude %>% 
  st_buffer(.00003)

streets_shopping <- st_read('{"type":"MultiLineString","coordinates":[[[-35.8703685,-7.23291530000001],[-35.8713144,-7.2317556],[-35.871363,-7.2317008],[-35.8714169,-7.23163870000001]],[[-35.8698282,-7.2324763],[-35.8701448,-7.23275],[-35.8703685,-7.23291530000001]],[[-35.8698282,-7.2324763],[-35.869413,-7.23213349999999],[-35.8684601248034,-7.23134389497677]],[[-35.8716661660622,-7.23150890216622],[-35.8715684,-7.2316271],[-35.8715036,-7.2317055],[-35.8714538,-7.2317688]],[[-35.8714169,-7.23163870000001],[-35.8715804415323,-7.23143954650213]],[[-35.8697518,-7.23382880000001],[-35.8703808,-7.23436810000001]],[[-35.8707694,-7.2338862],[-35.8701356,-7.2333642]],[[-35.8707694,-7.2338862],[-35.8703808,-7.23436810000001]],[[-35.8701844,-7.2333052],[-35.870828,-7.2338308]],[[-35.870828,-7.2338308],[-35.8721738,-7.23490689999999]],[[-35.8703808,-7.23436810000001],[-35.8717595,-7.2354543]],[[-35.8721123,-7.23498969999999],[-35.8707694,-7.2338862]],[[-35.8722308709866,-7.23508268461817],[-35.8721849,-7.2350463]],[[-35.8722507,-7.23496270000001],[-35.8722810083403,-7.23498757314507]],[[-35.8714538,-7.2317688],[-35.8701844,-7.2333052]],[[-35.8701844,-7.2333052],[-35.8701356,-7.2333642]],[[-35.8701356,-7.2333642],[-35.8697518,-7.23382880000001]],[[-35.8697518,-7.23382880000001],[-35.8688662,-7.2349007],[-35.8687669,-7.2350209],[-35.8684068,-7.23545670000001],[-35.8682294353325,-7.23567136942503]],[[-35.868152002584,-7.23560872232953],[-35.8682938,-7.2354445],[-35.8683924,-7.2353139],[-35.8685942,-7.2350744],[-35.8687093,-7.23493750000001],[-35.8687578,-7.2348774],[-35.8703685,-7.23291530000001]],[[-35.87207,-7.2322644],[-35.8716643,-7.2328065],[-35.8712714,-7.23328710000001],[-35.870828,-7.2338308]]]}', crs = 4326)

streets_shopping <- streets_shopping %>% 
  st_buffer(.00003)

streets <- st_union(streets_acude, streets_shopping)

drawings_resp$int_streets = st_intersects(drawings_resp %>% st_geometry(), streets, sparse = FALSE)
```

```{r}
as.data.frame(drawings_resp) %>% 
  filter(int_streets == TRUE) %>% 
  group_by(relation) %>% 
  summarise(true = sum(int_fun_c) / n(), false = (n() - sum(int_fun_c)) / n()) %>% 
  plot_ly(y = ~relation, x = ~true,  type = "bar", name = "Intersect the Function Result") %>% 
  add_trace(x = ~false, name = "Do not Intersect the Function Result") %>% 
  layout(barmode = "stack")
```

If we now only consider the drawings that intersect streets, the percentage
of drawings that our algorithm generated areas intersect is bigger for all 
spatial relations.

## Jaccard's Similarity Coefficient

A common metric used to access the similarity between sets is the Jaccard's 
Similarity Coefficient. It expresses how similar two sets are in a scale of 0 to 1.

Jaccard (A, B) = Area Of Intersection(A, B) / Area Of Union(A, B)

We can use this metric, to evaluate how similar are the geometries produced by 
the algorithms and the drawings made by the participants.

```{r}
jaccard_sim <- function(geom_a, geom_b){
    if(st_intersects(geom_a, geom_b, sparse = FALSE)){
      area_of_intersection = st_area(st_intersection(geom_a, geom_b))
    }else{
      area_of_intersection = set_units(0, m^2)
    }
    return(drop_units((area_of_intersection/st_area(st_union(geom_a, geom_b)))))
}

drawings_resp <- drawings_resp %>% 
  rowwise() %>% 
  mutate(jaccard = jaccard_sim(get_fun_geom(relation, landmark), geometry)) %>% 
  st_as_sf()

as.data.frame(drawings_resp) %>% 
  plot_ly(x = ~relation, y = ~jaccard, type = "box")

```

## Similarity with Intersection Between Drawings and Streets

If we again consider only the drawings that intersect the streets, we can now crop
the drawings and discard the portions that do not intersect streets to make a 
more fair comparison of areas.

```{r}
drawings_resp_int_streets <- drawings_resp %>% 
  filter(int_streets == TRUE)

drawings_resp_int_streets$geometry <- st_intersection(drawings_resp_int_streets$geometry, streets)
  
drawings_resp_int_streets <- drawings_resp_int_streets %>% 
  rowwise() %>% 
  mutate(jaccard = jaccard_sim(get_fun_geom(relation, landmark), geometry)) %>% 
  st_as_sf()

# Considering the ones where there is an intersection
drawings_resp_int_streets <- drawings_resp_int_streets %>% 
  filter(int_fun_c == TRUE)

as.data.frame(drawings_resp) %>%
  filter(int_fun_c == TRUE) %>% 
  plot_ly(x = ~relation, y = ~jaccard, type = "box", name = "Before Intersectiion") %>% 
  add_trace(x = ~drawings_resp_int_streets$relation, y = ~drawings_resp_int_streets$jaccard,
            name = "After Intersection") %>% 
  layout(boxmode = "group")
```

Comparing the areas with only the parts of drawings that intersect streets yields better results
even though most similarity values continue to be bellow .5. This might be an indicative of how hard this
problem is.

[TALK ABOUT ENTRE]

## Median Similarity Amonst Drawings

Lets examine the median similarity amonst the drawings themselves. To do this, we separate drawings by
landmark and relation and then for each drawing, compute the jaccard similarity index between it and all the
others in the same relation and landmark. The _inner jaccard_ is the median value of these indexes.

```{r}
all_rows_except <- function(rel, land, exc_id){
  return(drawings_resp %>%
           filter(relation == rel & landmark == land & id != exc_id) %>%
           st_geometry())
}
```


```{r}
drawings_resp <- drawings_resp %>% 
  rowwise() %>% 
  mutate(inner_jaccard = (jaccard_sim(geometry,
                                      all_rows_except(relation, landmark, id))) %>% median())

as.data.frame(drawings_resp) %>%
  filter(int_fun_c == TRUE) %>% 
  plot_ly(x = ~relation, y = ~inner_jaccard, type = "box") %>% 
  layout(yaxis = list(range = c(0, 1)))
```

In fact, we can observe that the drawings made by different participants are not very simillar.
In the future, different experiment setups might allow for a better use of this metric.

Nevertheless, the similarity indexes coupled with the intersection percentages show
that the proposed algorithms represent a good approach to the implementation of
directional spatial relations that are in accordance with the way people understand 
spatial language.